\documentclass{article}
\usepackage[utf8]{inputenc}


\title{Exploration and Presentation - Assignment 2 - Task 1}
\author{Martin Høigaard Rasmussen }
\date{March 2021}

\usepackage{natbib}
\usepackage{graphicx}

\begin{document}

\maketitle

\section{Requirements of bachelor thesis}

\subsection{Report \cite{bachelorProject}}
\begin{enumerate}
    \item Length: The maximum page count for the bachelor report is given by
the formular maxPageCount = 40 + 20 · numberOfStudents
 
    \item Language: The report can be written in either Danish or English.
    \item Contents : The report should contain a thorough description of the work that
has been done during the bachelor project, as well as an evaluation and reflection
on the work.
\end{enumerate}

\subsection{Report requirements \cite{bachelorProject}}
\begin{enumerate}
    \item The project has to have a cover page: Project title, your name and student identification,
school and supervisor.
    \item Abstract - Four sentences: Problem statement, further elaborated in Introduction. It can be seen as an advertisement for the rest of the report. The final
abstract is written in the end of the project.
    \begin{itemize}
    \item What is the problem? 
    \item Why is the problem interesting? 
    \item What is the solution? 
    \item What are the implications of the solution?

    \end{itemize}
    \item Introduction
    \begin{itemize}
        \item Motivation - why is this topic important
        \item Project objectives - What is the project supposed to achieve.
        \item Project tasks - What is being done to achieve the objectives.
        \item Scope - What is not included in the project.
        \item A Brief description of each chapter - One paragraph each. 
    \end{itemize}
    \item State of the art and trends : An overview and comparison of alternative development methodologies, technologies, environments, frameworks, or programming
languages that could have been used and explanation of your choice.

\item Solution development and implementation : "Presentation of the application, test procedures, deployment and maintenance environments: This part
presents the product in technical terms. Implementation and test environment
— test strategies, test plan, test suites, demo and screen captures, usability
evaluation, etc. Units of code, packages, deployment, supported interfaces, algorithms, input and output, supported file formats, frameworks, servers and
clients, etc.
" \cite{bachelorProject}

\item Conclusions : "Brief summary: What has been done and the benefits of it.
Recommendation for future extensions and upgrades. Reflection on the work
and the product." \cite{bachelorProject}

\item Appendices : List of information sources (litterature, source code, user manuals), as many as possible, listed according to a standard.

\end{enumerate}


\bibliographystyle{plain}
\bibliography{references}
\end{document}
